---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# farspackage

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/MagdyLaban/Building_R_Packages_Coursera.svg?branch=master)](https://travis-ci.org/MagdyLaban/Building_R_Packages_Coursera)
<!-- badges: end -->

```{r setup}
library(farspackage)
```
This package contains functions that read US National Highway Traffic Safety Administration's **Fatality Analysis Reporting System (FARS)** data and summarize them

* ## Reading in
For reading the complete file use: **fars_read(filename)**. It reads a CSV file and creates a tibble from it. Specify the filename using the **filename** argument .
argument.
* ## Making file name
To make a file you have to use **make_file(year)** and specify an integer value for **year** argument .

* ## Filtering
The **fars_read_years(years)** function takes a numeric value as **years** argument and returns a list of tibbles consisting of two columns: **MONTH** and **year**.

* ## Summarizing
The **fars_summarize_years(years)** function summarizes accidents for the specified **years**, grouped by **months**.

* ## Plotting
To plot the data for the specified state in the specified year you have to use the **fars_map_state(state.num, year)** function . **state.num** represents the state number and it takes a numeric value and **year** represents which year the accidents had token place and it is a numeric value .

